---
title: "Untitled"
author: "Katherine Rosencrance"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
```

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```

### Create  a subset with four cities

create subset that only contains obs where the city is 
-san luis obispo
-atascadero
-arroyo grande
-santa maria orcutt

```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```

### little exploration

Task create a summary table that has mean and standard deviation of home price grouped by city and sale status

```{r}
homes_table <- homes_subset %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price),
            sd_price = sd(Price))
homes_table
```
Task explore relationship between sqaure footage and price

```{r}
homes_subset %>% 
  ggplot(aes(x = SqFt, y = Price ))+
  geom_point()+
  geom_smooth(method = "lm")
```
use multiple linear regression to investigate realtionships between several predictor variables and home price

create 2 diff permutations of this model

1. price- city, bedrooms, bathrooms, sqft, and status (lm1)
2. price- city, sqft, status (lm2)
3. try another one (lm3)

```{r}

lm1 <-lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)

lm2 <- lm(Price ~ SqFt + City + Status, data = homes_subset)

lm3 <- lm()

## if i wanted San Luis Obispo to be the reference level: use fct_relevel to specify a new reference level

  
```


## explore correlations beetween quantitative variables

mask subset called homes_quant from homes subset that only contains variables from price- sqft

```{r}
homes_quant <- homes_subset %>% 
  select(Price, Bedrooms, Bathrooms, SqFt)

homes_cor <- cor(homes_quant)

corrplot(homes_cor)
```
### COmpare AIC values

```{r}
AIC(lm1)
AIC(lm2)
```

# lower aic indicates better
### Use model summary to return multiple model outputs

```{r}
modelsummary(list(lm1, lm2))
```

### Check out diagnostic plots for lm1

```{r}
plot(lm1)
```
use broom::augment to return the predictions for existing obs

```{r}
home_predictions <- augment(lm1)

ggplot(data = home_predictions, aes(x = .resid))+
  geom_histogram()
```
# BRANCHES WOO
